%-------------------------
% Resume in Latex
% Author : Ajay Gowda
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5} \usepackage{multicol} \usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage{mathptmx}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}


\newcommand{\resumeSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\

    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\large#1} & \textit{\small #2} \\

    \end{tabular*}\vspace{-1pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Ajay Gowda} \\ \vspace{1pt}
    Amsterdam, Netherlands \\ \vspace{1pt}
    \small \href{tel:+31645353160}{ \raisebox{-0.1\height}\faPhone\ \underline{+31-645353160} ~}
    \href{mailto:ajaysgowda@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ajaysgowda@gmail.com}} ~
    \href{https://linkedin.com/in/ajaysgowda}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{ajaysgowda}}  ~
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {EVBOX}{Amsterdam, NL}
    \resumeSubSubHeadingListStart
      \resumeSubSubheading
        {\underline{Systems Validation Engineer}}{Sep 2020 - Present}
      \resumeItemListStart
        \resumeItem{\normalsize{Design, develop and execute automated firmware tests to validate system requirements
        like OCPP and IEC-61851 / ISO-15118 compatibility, happy/unhappy paths, and custom features.}}
        \resumeItem{\normalsize{Develop, deploy and maintain data acquisition infrastructure like databases, visualization tools and vpns on AWS.}}
        \resumeItem{\normalsize{Design and develop one off test setups for unique test scenarios including data acquisition and generating reports.}}
        \resumeItem{\normalsize{Design and develop test benches for correct and repeatable hardware and software validation and verification.}}
        %\resumeItem{\normalsize{Assist customers with highly customized charging infrastructure implementation.}}
        \resumeItem{\normalsize{Assist with pre-compliance testing for certifications such as Energy Star and UL.}}
        \resumeItem{\normalsize{Develop and maintain EOL (End of Line) test applications.}}
      \resumeItemListEnd
    \resumeSubSubHeadingListEnd

    \resumeSubheading
      {ETERNAL SUN SPIRE}{The Hague, NL}
    \resumeSubSubHeadingListStart
      \resumeSubSubheading
        {\underline{Development and Validation Engineer}}{Aug 2018 – Jul 2020}
      \resumeItemListStart
        \resumeItem{\normalsize{Troubleshoot issues with prototype and production photovoltaic Test Equipment in
        Labs and Manufacturing lines.}}
        \resumeItem{\normalsize{Work with customers on development projects which involved fixing critical issues, adding features
        and tuning prototype machines.}}
        \resumeItem{\normalsize{Design and develop control architecture for photovoltaic test machines to enable optimal
        performance and data acquisition.}}
      \resumeItemListEnd
    \resumeSubSubHeadingListEnd

    \resumeSubheading
      {GENERAL MOTORS}{Milford, USA}
    \resumeSubSubHeadingListStart
      \resumeSubSubheading
        {\underline{Hybrid Powertrain Development Engineer}}{Jan 2016 -- Aug 2018}
      \resumeItemListStart
        \resumeItem{\normalsize{Develop efficient powertrains with optimal fuel economy and exceptional performance
              via work on batteries, motors,hydraulic systems, internal combustion engines, and power electronics.}}
        \resumeItem{\normalsize{Ensure vehicle test fleet is up to date with latest hardware and software.}}
        \resumeItem{\normalsize{Collect and analyse data from vehicles on test tracks, in extreme locations,
              and state of the art high feature test cells using vehicle monitoring software and hardware.}}
        \resumeItem{\normalsize{Validate new hybrid and electric powertrains subjectively and objectively.}}
        \resumeItem{\normalsize{Ensure vehicle test fleet is up to date with latest hardware and software.}}
        \resumeItem{\normalsize{Construct one-off wiring harnesses that include high voltage and CAN communication loops.}}
      \resumeItemListEnd

      \resumeSubSubheading
        {\underline{Algorithm Development Engineer – Thermal Controls}}{Jul 2015 -- Jan 2016}
      \resumeItemListStart
        \resumeItem{\normalsize{ Develop thermal control system for liquid cooled High Voltage battery systems.}}
        %\resumeItem{\normalsize{Software functionality test using SIL and HIL testing techniques.}}
      \resumeItemListEnd
    \resumeSubSubHeadingListEnd

    \resumeSubheading
      {UNIVERSITY OF WASHINGTON}{Seattle, USA}
    \resumeSubSubHeadingListStart
      \resumeSubSubheading
        {\underline{Research Assistant at EcoCAR Laboratory}}{Oct 2013 -- Jun 2015}
      \resumeItemListStart
        \resumeItem{\normalsize{Build, run and assess hybrid powertrain configurations for real world feasibility}}
        \resumeItem{\normalsize{Worked on control logic of the supervisory controller that interlinks the two powertrains. (Electric and Diesel)}}
      \resumeItemListEnd
    \resumeSubSubHeadingListEnd


  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UNIVERSITY OF WASHINGTON}{Seattle, USA}
    \resumeSubSubHeadingListStart
      \resumeSubSubheading
        {Master of Science in ME, Control Systems}{Sept 2013 -- May 2015}
      \resumeItemListStart
        \resumeItem{\normalsize{Linear Controls, Digital controls, Optimal Controls}}
        \resumeItem{\normalsize{Master’s Thesis - System Level Modeling and Simulation of a Hybrid Vehicle.}}
      \resumeItemListEnd
    \resumeSubSubHeadingListEnd

    \resumeSubheading
      {MANIPAL INSTITUTE OF TECHNOLOGY}{Manipal, India}
    \resumeSubSubHeadingListStart
      \resumeSubSubheading
        {Bachelor of Science in Mechatronics Engineering}{June 2009 -- May 2013}
      \resumeItemListStart
        \resumeItem{\normalsize{Control Theory, Analog and digital circuit design, Embedded Systems, PLC, Hydraulic and Pneumatic systems.}}
      \resumeItemListEnd
    \resumeSubSubHeadingListEnd
  \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{Python, MATLAB/ Simulink, JAVA, C/C++, TypeScript, HTML, Structured Text (PLC),YAML, XML, SQL}} \\
     \vspace{4pt}
     \textbf{\normalsize{Technologies: }}{\normalsize{AWS, Big Query, Grafana, Influxdb, Wireguard, Docker, Linux, ARM, GIT, Polarion}} \\
     \vspace{4pt}
     \textbf{\normalsize{Frameworks: }}{\normalsize{FastAPI, Django, pytest, opencv, pymodbus, socketCAN}} \\
     \vspace{4pt}
     \textbf{\normalsize{Automotive industry tools: }}{\normalsize{MDA, INCA, Vehicle Spy, dSPACE, neoVI, High Performance Driver Education from GM}} \\
     \vspace{4pt}
     \textbf{\normalsize{Standards: }}{\normalsize{OCPP 1.6, OCPP 2.0, ISO-15118, IEC-61851, MODBUS, CAN, REST API, Websockets,
     OPC UA, OBD2, EEBUS}} \\
    }}
 \end{itemize}
\vspace{-10pt}


\end{document}

